\chapter{Acknowledgments}\label{chap:acks}

\chapterQuote{\textit{``Appreciation is a wonderful thing. It makes what is excellent in others belong to us as well.''}}{--- Voltaire}

\chapterAbstract{A}{lthough this chapter is one that contains no information about the topics found throughout the rest of the pages of this book, it finds itself dear and near to my heart, as my time as a student comes to its end, a new page on the book of my life draws near. I take this opportunity to be grateful for the amazing people I have found along the way.

First and foremost I extend my most sincerest gratitude to my directors Inma and Dani, the people who have been closest to the development of these works and have helped shape the words you are about to read. They are leaders by example and whom without I would have found myself lost on a multitude of occasions, all while having the utmost respect and understanding of everyone around them. And to David, our director, I say thank you for the trust and confidence you have instilled in me on many more than one occasion, even in times I did not trust in myself, your enthusiasm and true passion for research and advancement of the fields you work on is inspirational and I feel very lucky to be working alongside all of them.

To the people who have accompanied me on the daily throughout the days, my colleagues Agustin, Fernando, Pepe and Paula with whom I have shared our own small piece of the university halls where, not so long ago, we were students (some still are), I thank them for all the great times, coffee break conversations, debates and brainstorms we have shared throughout or time together. You are what gave me a reason to visit that room on the second floor of module F, I wish every single one of you the very best in your endeavors and that you accomplish whatever your brilliant minds decide to pursue next, although I have no doubts about your success.

To my friends, who kept me sane during these times, took my mind off of my duties when needed giving me a moment of respite, pushed me to continue when I faltered and had the patience to stand by my side through all, I appreciate all you being there.

And my most heartfelt thanks go to the people closest to me, to those who pushed me every step of the way, who picked me up every time I fell down and who always are there when I need them, my parents, whose interest In my progress was only peaked by their interest in my wellbeing and their unwavering love and support. And finally, to Blanca, for an infinitely long list of reasons which I am unable to fit in these pages for fear this book would become a trilogy instead.

To all of you, thanks.
}
