\chapter{Abstract}\label{chap:abstract}

\chapterQuote{\hfill\textit{``Brevity is the soul of wit.''}}{--- \textit{Hamlet}, William Shakespeare}

\chapterAbstract{N}{owadays, Knowledge Graphs are a widely used means to store structured information for a variety of different domains and applications. However, due to the fact that they are usually constructed using automated information extraction techniques, they are often incomplete, either because these techniques failed to extract the relevant information, or because it was not present altogether in the original sources. 

The problem that we address in this dissertation is how to find this missing knowledge and complete Knowledge Graphs in an automatic manner. In the literature, there are already many proposals to perform this task. However, they have important drawbacks, namely: they rely on embedded representations, which are computationally expensive to generate and demand frequent regenerations, they require human intervention or human-provided data, they rely on external sources of information, they cannot produce new knowledge on their own, or they do not scale properly to very large Knowledge Graphs. 

In this dissertation, we present a new automated proposal for completing Knowledge Graphs that does not suffer from any of the previous drawbacks. Our contribution is threefold: CHAI, a technique for automatically generating tractable sets of candidate triples; CAFE, a high-accuracy triple classification proposal; and SciCheck, a technique specifically tailored for completing scientific Knowledge Graphs. Our theoretical and practical validation suggests that our proposal is very efficient and effective in practice, and that it is able to successfully complete Knowledge Graphs of varying natures.}